Draft Documents

### 2022-10-30 src/draft.Rmd
Layouts

1.  **Use complete cases**: Only use the complete cases for the analysis. This is a straightforward approach, but doesn't resolve the bias resulted from the mass loss of data.
2.  **Step-by-step remove frequently missing variables**: The same as we did before, but this process should be carried out carefully as we run the chance of dropping an important variable.
3.  **Update the data set as we select variables**: As we drop insignificant variables (in backward selection), the number of NAs are changed as well. We can utilize the extra complete cases to build the next model in the steps.
4.  **Imputation**: The idea is to replace the missing observations on the response or the predictors with artificial values that try to preserve the data set structure. This is a quite complex topic of its own, but we think why not. You can read more at from @imputation.

## 2.3. Descriptive Analytics

## 2.4. Data Source

@@

>>>>

1.  **Use complete cases**: Only use the complete cases for the analysis. This is a straightforward approach, but doesn't resolve the bias resulted from the mass loss of data.
2.  **Selectively remove variables with high missing rate**: The same as we did before, but this process should be carried out carefully as we run the chance of dropping an important variable.
3.  **Update the data set as we select variables**: As we drop insignificant variables (in backward selection), the number of NAs are changed as well. We can utilize the extra complete cases to build the next model in the steps.
4.  **Imputation**: The idea is to replace the missing observations on the response or the predictors with artificial values that try to preserve the data set structure. This is a quite complex topic of its own, but we think why not. You can read more at from @imputation.

## 2.3. Descriptive Analytics
(To be done)
## 2.4. Data Source

@@

# 3. Model Selection and Interpretation
## 3.1. Assumption Check (To be done)

## 3.2. Ordinary Multiple Linear Regression

We conduct a normal linear regression, following the approaches mentioned above to address missing values issues.

### 3.2.1. Use Complete Cases (To be done)
#### 3.2.1.1. Model Fitting
#### 3.2.1.2. Assessment
#### 3.2.1.3. Interpretation

### 3.2.2. Selectively remove variables with high missing rate (To be done)
#### 3.2.2.1. Model Fitting
#### 3.2.2.2. Assessment
#### 3.2.2.3. Interpretation

### 3.2.3. Update the data set as we select variables (To be done)
#### 3.2.3.1. Model Fitting
#### 3.2.3.2. Assessment
#### 3.2.3.3. Interpretation

### 3.2.4. Imputation (To be done)
#### 3.2.4.1. Model Fitting
#### 3.2.4.2. Assessment
#### 3.2.4.3. Interpretation

## 3.3. Panel Data Analysis (To be done)

# 4. Conclusion
# 5. Appendix
# 6. References
